### 2021-04-14 paper.Rmd
Comment in the Intro about UMAP

>>>>

<!-- Reading the introduction I noticed maybe can be included UMAP, I'm not an expert (Uniform Manifold approximation and projection for dimension reduction ) I saw this before but maybe some of you know about it to evaluated if worth it to be include it here. I have an arXiv paper https://arxiv.org/abs/1802.03426 maybe some of you can identify if it is relevant or not or at least you know about the authors ....just a comment (Di, or ALL )-->
